Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-29 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
Pass at intro and conclusion. Suggestions for shortening

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores.

@@

  Next, we generalize Markov state models, treating the
  configurational states of the system as a Markov process where each
  state has distinct transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative differences 
  between MD and Markov state dependent model-generated trajectories may limit 
  its usefulness.

  Finally, we demonstrate how one can use these models to 
  estimate flux of a solute across a macroscopic-length pore and, based on 
  those quantities, the membrane's selectivity towards each solute. This work 
  helps to connect microscopic chemically-dependent solute motions that do not
  follow simple diffusive behavior with macroscopic membrane performance.

@@

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to produce 
  at scale.~\cite{hatakeyama_nanoporous_2010}

  Molecular modeling may make it possible to efficiently evaluate
  solute-specific separation membranes using the available chemical space of
  LLC monomers. To date, only a limited subset of LLC monomers have been
  studied experimentally in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
  can provide the resolution necessary to identify molecular interactions that
  are key to separation mechanisms, allowing us to move beyond Edisonian design
  approaches.

@@

  Up through our previous studies, our molecular models have provided valuable
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they
  would be of greater value to a larger set of researchers if we could provide
  quantitative predictions of macroscopic observables such as solute flux and
  selectivity. Due to the size of the types of systems we are studying (at
  least 62,000 atoms) it is prohibitively expensive and time-consuming to run
  simulations longer than those performed for this work ($\sim$5 $\mu$s). Even
  with the relatively large size of our system, we only simulate 24 solute
  trajectories per unit cell in order to minimize solute-solute interactions.
% BJC2: removed this sentence. High uncertainty MSDs don't really relate to long timescale predictions. Unless the MSDs were linear.
%  This results in relatively high uncertainties in observables such as mean
%  squared displacement (MSD), preventing reliable long timescale predictions.
  We are in need of an efficient method which can use our limited atomistic 
  simulation data sets in order to predict long timescale solute behavior.  
  %BJC2: following sentence replaced with above
%  We are in need of a way of studying the collective motion of a much larger
%  set of solutes over much longer timescales.
  %MRS11: Maybe this last sentence could be changed. Because you aren't really finding a way to study larger sets of 
  %solutes over larger timescales, you are using a limited amount of atomistic simulation into long time scale behavior efficiently. We can discuss variations as needed!

  %BJC: maybe this paragraph can be cut down?
  Mathematical descriptions of transport in complex separations membranes are a
  powerful way to understand mechanisms and formulate design principles.
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  %MRS11: this next sentence could probably be cut - it's kind of vague.
  %BJC2: True
%  The complexity of a well-fit model generally parallels the complexity of the
%  transport mechanism being studied, as well as the transport information the
%  model conveys. 
  In dense homogeneous membranes, the solution-diffusion model
  can extract diffusion and partition coefficients and has successfully
  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
  Analogously, pore-flow models yield predictions of diffusion coefficients and
  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
  Modern single particle tracking approaches have taken researchers beyond
  continuum modeling allowing them to characterize complex diffusive
  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
  molecular dynamics (MD) simulations to study both single particle dynamics
  and bulk transport properties with atomic-level
  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
  approaches facilitate generation of hypotheses about the molecular origins of
  separations by attempting to give a more intuitive understanding of how
  solutes move as a function of their environment, in turn suggesting
  experiments that could be performed.

  %MRS11: in this paragraph, the ``we can'' is vague, and doesn't
  %ascribe agency.  Is ``We'' our group? Is it the field as whole?
  %If it's something someone has done in the past, there should be
  %citations. If it's something that can be done in the future, the
  %phrasing should be a long the lines of ``it is possible to'', ``it
  %can be done'', etc.

  Using a bottom-up modeling approach, it may be possible to parameterize single
  particle behavior by extracting particle trajectories from MD simulations and
  studying the properties that have the greatest influence on solute dynamics.
  With this information, one can learn how to construct an ensemble of characteristic
  single solute trajectories with these properties which would be useful for
  making long timescale predictions with computational ease and lower
  uncertainties. Fortunately, there is an abundance of information encoded in
  the complex solute trajectories. One can incorporate fluctuations and 
  time-dependent correlations in solute position into transport models, 
  as well as the length of time solutes are trapped. It is possible to add further
  detail by integrating this time series analysis with existing knowledge of the
  primary trapping mechanisms as well as the solute's changing chemical environment
  within the heterogeneous membrane.

@@

  % BJC: I'd say this is where the intro starts to get technical
%  We constructed our first model by applying the existing rigorous theoretical
%  foundation which describes the motion of particles that exhibit non-Brownian,
%  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
%  introduced by fractional calculus are instrumental to this
%  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
%  normally linear diffusion equation to fractional derivative orders, providing
%  descriptions of a much more diverse set of behavior, including subdiffusion,
%  a type of anomalous diffusion exhibited by solutes in this
%  study.~\cite{klages_anomalous_2008}

  %MRS11: should be clear if first model is previous publications, or what is presented here.
  %If what is presented here, should talk about how it will be presented, not that it was developed. 
  %MRS11: research activities happened in the past, presentation of research is described in the present.
  %or potentially future if describing what will be presented in the rest of the paper. 
  %BJC: replacement to above.
  %BJC1: Made clear that this is talking about the first model of this work.
  %BJC1: went through rest of intro to make sure tense is consistent
  The first model that we develop in this work allows us to characterize the 
  hopping and trapping behavior displayed by solutes in our MD simulations. This 
  type of non-Brownian dynamical behavior results in subdiffusive transport which
  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
  %MRS12: removing paragraph break
  % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
  % stole thesis from paragraph below it
  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

%  Three well-known classes of behavior leading to anomalous subdiffusion are
%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
%  motion are frequently used alone or in combination to describe single
%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
%  is characterized by a distribution of hop lengths and dwell times, where
%  trajectories consist of sequential independent random draws from each
%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
%  viscoelastic environments where each jump comes from a Gaussian distribution
%  but is anti-correlated to its previous
%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
%  dead ends cause anti-correlated
%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

@@

  Where sufficiently close to observed data, these fitted sFBM models
  provide a way to propagate information about solute trajectories gathered 
  at the microsecond time scale to realistic experimental time scales. 
  They can also confirm the importance of assumed solute-membrane interactions 
  used to define the model's functional form, and
  suggest missing components. They can help researchers formulate hypotheses to
  explain why a certain set of parameters is characteristic to a specific
  solute.

@@

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data. We ran MD simulations using the leapfrog integrator with 
  hydrogen bonds constrained by the LINCS algorithm. We simulated a time step of 2 fs at
  a pressure of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and
  the v-rescale thermostat respectively. We recorded frames every 0.5 ns.

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. In this work, we only consider the MSD with respect to
  the solutes' center of mass $z$-coordinate, which is oriented along the pore 
  axis. A value of $\alpha < 1$ indicates a subdiffusive process, while values
  of $\alpha = 1$ and $\alpha > 1$ are characteristic of Brownian and 
  superdiffusive motion respectively.

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Rather than using them to calculate 
  diffusion constants or to relate our simulations to experimental measurements, we
  compare MSDs calculated from MD simulations to those generated from our models 
  in order to validate those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories.

@@

  There are many methods for estimating the Hurst parameter for a time series.
  \cite{clegg_practical_2006} It can be a difficult task because 
  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
  $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten 0.5 ns time lags of the empirically measured autocorrelation function.

@@

%BJC8: from author guidelines. Should there only be a line between column headings?
%Use a single horizontal rule to separate the column headings from the entries in the table. Use horizontal space within the body of the table to separate broad groups of entries. Extra vertical space may be used between columns. Avoid vertical rules in tables. Use lower-case roman letters for footnotes placed at the bottom of a table.
%MRS9: I'd go with what they said.  Looking at PRE, it looks like you can put double lines above and below the table, though - I added them 
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate hop correlation 
	  into all models.}\label{table:anomalous_models}

@@

  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}

@@

  \subsubsection{Model predictions}\label{section:AD_all_data}

  We obtain reasonable predictions of the MD simulated MSDs when we
  parameterize AD models with all available data after the perceived
  equilibration time. The MSD curves generated from both the one and 
  two mode models are overlayed with the MD simulated MSDs for comparison in
  Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
  mode models are presented in Figures~\ref{fig:1mode_parameters}
  and~\ref{fig:2mode_parameters}.

@@

  We have tested two different mathematical frameworks for describing solute
  motion by applying them to an H\textsubscript{II} phase LLC membrane. The
  values obtained for the parameters when fitting the models to the time series
  data offer important mechanistic insight on the molecular details of
  transport. Subordinated fractional Brownian and L\'evy motion have a strong
  theoretical foundation in the anomalous diffusion literature. Our single mode
  AD model quantifies and allows comparison of the hopping and trapping behavior
  among solutes. A two mode model that describes dynamics based on whether a
  solute is in or out of the pore region allows us to break down individual
  solute motion into the two distinct regimes and we showed that solute motion
  is clearly restricted while in the tail region. Our Markov state-dependent
  dynamical model uses explicitly defined trapping mechanisms and gives a nice
  description of transitions between these observed states, the equilibrium
  distribution of solutes among states as well as the type of stochastic
  behavior shown in each state.

>>>>

  Mathematically modeling complex transport phenomena can be a
  powerful tool for extracting important physical information from 
  molecular simulations. In this study, we present two new approaches 
  that use stochastic time series modeling to predict long-time scale 
  behavior and macroscopic properties from molecular simulation which
  can be generalized to other molecular systems where complex diffusion
  occurs.
  %BJCA: eliminated repetition and merged paragraphs, since the following is one sentence
  %In this study, we use two different stochastic time series modeling approaches parameterized 
  Specifically, we parameterize our models using long molecular dynamics (MD) simulation
  trajectories of a cross-linked H\textsubscript{II} phase lyotropic liquid
  crystal (LLC) membrane in order to predict solute mean squared displacements (MSDs)
  and solute flux, and thus solute selectivity, in macroscopic length pores.

@@

  Next, we present an approach that generalizes Markov state models,
  treating the configurational states of the system as a Markov
  process where each state has distinct transport properties. For each
  state and transition between states, we parameterize the
  distribution and temporal correlation structure of positional
  fluctuations as a means of characterization and to allow us to
  predict solute MSDs. 
  %BJCA: should we add a pargraph break here? Kind of short, but doesn't quite fit with above
  We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative
  differences between MD and Markov state dependent model-generated
  trajectories may limit its usefulness.

  Finally, we demonstrate how one can use these models to estimate
  flux of a solute across a macroscopic-length pore and, based on
  those quantities, the membrane's selectivity towards each
  solute. This work therefore helps to connect microscopic,
  chemically-dependent solute motions that do not follow simple
  diffusive behavior with long-time scale behavior, in an approach
  %BJCA: should hyphen in long-time scale be there? I would favor the pronunciation that goes with long time-scale with or w/o the hyphen
  generalizable to many kinds of molecular systems with complex dynamics.

@@

  % BJCA: Would it make more sense to have the first paragraph less
  % applications-focused and more centered around a need for our new methods?
  % Something like .. 
  There is a large disparity between the time scales accessible to atomistic
  molecular dynamics (MD) simulations and experiment.
  \begin{itemize}
    \item The dynamics of molecules over nanoseconds of simulation may
    tell a very different story than that inferred by bulk measurements
    on the time scale of seconds.
    %BJCA: can cite something about different diffusive regimes 
    \item Understanding complex dynamical behavior on short timescales 
    and connecting them with much longer timescales can provide 
    fundamental insight which can be used for atomic level design of
    materials.
    \item In this work, we pursue this connection applied to highly 
    selective aqueous filtration membranes and demonstrate how one can
    gain chemical intuition which serves both theoretical and 
    experimental researchers.
  \end{itemize}

@@

  % BJCA: I could likely condense this paragraph to focus primarily on the HII phase
  % and its complex pores.
  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to produce 
  at scale.~\cite{hatakeyama_nanoporous_2010}

  Molecular modeling may make it possible to efficiently evaluate
  solute-specific separation membranes using the available chemical space of
  LLC monomers
  %BJCA added rest of sentence:
  by allowing us to understand their macroscopic behavior based on microscopic, chemically-dependent solute motions.
  To date, only a limited subset of LLC monomers have been
  studied experimentally in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
  can provide the resolution necessary to identify molecular interactions that
  are key to separation mechanisms, allowing us to move beyond Edisonian design
  approaches.

@@

  Up through our previous studies, our molecular models have provided valuable
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they
  would be of greater value to a larger set of researchers if we could provide
  quantitative predictions of macroscopic observables such as solute flux and
  selectivity. Due to the size of the types of systems we are studying (at
  least 62,000 atoms) it is prohibitively expensive and time-consuming to run
  simulations longer than those performed for this work ($\sim$5 $\mu$s). Even
  with the relatively large size of our system, we only simulate 24 solute
  trajectories per unit cell in order to minimize solute-solute interactions.
  We are in need of an efficient method which can use our limited atomistic 
  simulation data sets in order to predict long timescale solute behavior.

  %BJCA: maybe this paragraph can be cut down?
  Mathematical descriptions of transport in complex separations membranes are a
  powerful way to understand mechanisms and formulate design principles.
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  In dense homogeneous membranes, the solution-diffusion model
  can extract diffusion and partition coefficients and has successfully
  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
  Analogously, pore-flow models yield predictions of diffusion coefficients and
  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
  Modern single particle tracking approaches have taken researchers beyond
  continuum modeling allowing them to characterize complex diffusive
  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
  molecular dynamics (MD) simulations to study both single particle dynamics
  and bulk transport properties with atomic-level
  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
  approaches facilitate generation of hypotheses about the molecular origins of
  separations by attempting to give a more intuitive understanding of how
  solutes move as a function of their environment, in turn suggesting
  experiments that could be performed.

  Using a bottom-up modeling approach, it may be possible to parameterize single
  particle behavior by extracting particle trajectories from MD simulations and
  studying the properties that have the greatest influence on solute dynamics.
  With this information, one can learn how to construct an ensemble of characteristic
  single solute trajectories with these properties which would be useful for
  making long timescale predictions with computational ease and lower
  uncertainties. 
  %Fortunately,
  There is an abundance of information encoded in
  the complex solute trajectories. One can incorporate fluctuations and 
  time-dependent correlations in solute position into transport models, 
  as well as the length of time solutes are trapped. It is possible to add further
  detail by integrating this time series analysis with existing knowledge of the
  primary trapping mechanisms as well as the solute's changing chemical environment
  within the heterogeneous membrane.

@@

  % BJCA: resurrected this paragraph
  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes in this on the simulation 
  time scales of this study.~\cite{klages_anomalous_2008}
  % BJCA: removing less technical version of above
%  The first model that we develop in this work allows us to characterize the 
%  hopping and trapping behavior displayed by solutes in our MD simulations. This 
%  type of non-Brownian dynamical behavior results in subdiffusive transport which
%  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
  %MRS12: removing paragraph break
  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

%BJCA: I could replace above with this, but I think I like the above better. It's more concise.
%  Three well-known classes of behavior leading to anomalous subdiffusion are
%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
%  motion are frequently used alone or in combination to describe single
%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
%  is characterized by a distribution of hop lengths and dwell times, where
%  trajectories consist of sequential independent random draws from each
%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
%  viscoelastic environments where each jump comes from a Gaussian distribution
%  but is anti-correlated to its previous
%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
%  dead ends cause anti-correlated
%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

@@

  % BJCA: Is this paragraph needed? 
  Where sufficiently close to observed data, these fitted sFBM models
  provide a way to propagate information about solute trajectories gathered 
  at the microsecond time scale to realistic experimental time scales. 
  They can also confirm the importance of assumed solute-membrane interactions 
  used to define the model's functional form, and
  suggest missing components. They can help researchers formulate hypotheses to
  explain why a certain set of parameters is characteristic to a specific
  solute.

@@

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data. We ran MD simulations using the leapfrog integrator with 
  hydrogen bonds constrained by the LINCS algorithm. We simulated a time step of 2 fs at
  a pressure of 1 bar and 300K controlled by the Parrinello-Rahman barostat and
  the v-rescale thermostat respectively. We recorded frames every 0.5 ns.

@@

  On the time scales simulated in this study,
  solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. In this work, we only consider the MSD with respect to
  the solutes' center of mass $z$-coordinate, which is oriented along the pore 
  axis. A value of $\alpha < 1$ indicates a subdiffusive process, while values
  of $\alpha = 1$ and $\alpha > 1$ are characteristic of Brownian and 
  superdiffusive motion respectively.

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. It is also possible that solute dynamics will become diffusive on
  long simulation timescales. Therefore, the transition from subdiffusion to regular
  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD curves. 
  We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Rather than using them to calculate 
  diffusion constants or to relate our simulations to experimental measurements, we
  compare MSDs calculated from MD simulations to those generated from our models 
  in order to validate those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories.

@@

  There are many methods for estimating the Hurst parameter for a time series.
  \cite{clegg_practical_2006} It can be a difficult task because 
  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
  $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained $H$ by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten 0.5 ns time lags of the empirically measured autocorrelation function.

@@

  %BJCA: I could get rid of this table and define them in text. 
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate hop correlation 
	  into all models.}\label{table:anomalous_models}

@@

  %BJCA: maybe this to supporting?
  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  %BJCA: This section to supporting
  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}

@@

  % BJCA: could move 2 mode to SI
  \subsubsection{Model predictions}\label{section:AD_all_data}

  We obtain reasonable predictions of the MD simulated MSDs when we
  parameterize AD models with all available data after the perceived
  equilibration time. The MSD curves generated from both the one and 
  two mode models are overlaid with the MD simulated MSDs for comparison in
  Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
  mode models are presented in Figures~\ref{fig:1mode_parameters}
  and~\ref{fig:2mode_parameters}.

@@

  We have tested two different mathematical frameworks for
  %BJCA: rephrase
  % describing solute motion
  describing complex solute dynamics
  by applying them to an H\textsubscript{II} phase LLC membrane. The
  values obtained for the parameters when fitting the models to the time series
  data offer important mechanistic insight on the molecular details of
  transport. Subordinated fractional Brownian and L\'evy motion have a strong
  theoretical foundation in the anomalous diffusion literature. Our single mode
  AD model quantifies and allows comparison of the hopping and trapping behavior
  among solutes. A two mode model that describes dynamics based on whether a
  solute is in or out of the pore region allows us to break down individual
  solute motion into two distinct regimes and we showed that solute motion
  is clearly restricted while in the tail region. Our Markov state-dependent
  dynamical model uses explicitly defined trapping mechanisms and gives a nice
  description of transitions between these observed states, the equilibrium
  distribution of solutes among states as well as the type of stochastic
  behavior shown in each state.
